Equalizer\\Programming and User Guide

### 2012-06-26 Developer/ProgrammingGuide/paper.tex
Update appendix with new file format tokens

@@

{\footnotesize\lstinputlisting[firstline=89, lastline=98]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=100, lastline=109]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=111, lastline=129]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=130, lastline=139]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=141, lastline=162]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=163, lastline=172]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=177, lastline=183]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=185, lastline=188]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=188, lastline=209]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=212, lastline=237]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=239, lastline=260]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=262, lastline=333]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

>>>>

\begin{tabularx}{\textwidth}{|l|X|}
  \hline
  \textbf{Name} & EQ\_PIPE\_IATTR\_HINT\_AFFINITY\\
  \textbf{Value} & OFF \textbar \ AUTO \textbar \ CORE unsigned  \textbar
  \ SOCKET unsigned\\
  \textbf{Default} & AUTO\\
  \textbf{Details} & Determines how all pipe threads are bound to processing
  cores. When set to OFF, threads are unbound and will be scheduled by the
  operation system on any core. If set to AUTO, threads are bound to all cores
  of the processor which is closest to the GPU used by the pipe, that is, which
  have the lowest latency to access the GPU device. This feature requires that
  Lunchbox and Equalizer have been compiled with the hwloc library version 1.5
  or later. When set to CORE, the pipe threads will be bound to the given
  core. When set to SOCKET, the pipe threads will be bound to all cores of the
  given processor (socket). The CORE and SOCKET settings require that Lunchbox
  and Equalizer have been compiled with the hwloc library version 1.2 or
  later.\\ \hline
\end{tabularx}\\\vfill

@@

{\footnotesize\lstinputlisting[firstline=90, lastline=99]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=101, lastline=110]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=112, lastline=130]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=131, lastline=141]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=143, lastline=163]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=165, lastline=174]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=179, lastline=185]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=187, lastline=190]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=190, lastline=211]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=214, lastline=239]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=240, lastline=262]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}

@@

{\footnotesize\lstinputlisting[firstline=264, lastline=337]
  {../../../equalizergraphics/documents/design/fileFormat.shtml}}
